{\itshape Delineate urban boundaries in Great Britain from the network of Twitter user spatial interactions}

### 2016-02-20 urban_boundaries_gb/IJGIS/Paper.tex
new submission

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% fixltx2e package for \textsubscript
\usepackage{fixltx2e}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
\usepackage{rotating}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\graphicspath{ {/figures/} }
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

\usepackage[section]{placeins}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.35in}

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{Delineate urban boundaries in Great Britain from the network of Twitter user spatial interactions}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Junjun Yin\textsuperscript{1, 2, 3},
Aiman Soliman\textsuperscript{1, 2, 4},
Dandong Yin\textsuperscript{1, 2, 3},
Shaowen Wang\textsuperscript{1, 2, 3, 4, $\ast$}
\\
\bigskip
\bf{1} CyberGIS Center for Advanced Digital and Spatial Studies
\\
\bf{2} CyberInfrastructure and Geospatial Information Laboratory (CIGI)
\\
\bf{3} Department of Geography and Geographic Information Science
\\
\bf{4} National Center for Supercomputing Applications
\\
\bf{} University of Illinois at Urbana-Champaign, 61801, IL, USA
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note

% Current address notes
%\textcurrency a Insert current address of first author with an address update
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

% Deceased author note
%\dag Deceased

% Group/Consortium Author Note
%\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* shaowen@illinois.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns.
Defining the boundaries of urban regions is important to city planning, traffic management and resource allocation.
Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's daily interactions with the urban space in their intra- and inter regional activities.
In this study, we presented a method to redraw urban boundaries based upon human interaction with the physical space.
Specifically, we delineated the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million Twitter messages.
Our study connects human mobility research with the delineation of non-administrative anthropographic urban boundaries based on Twitter user spatial interactions, which provides a new understanding of the interactions between urban structure and human activity.
We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
The result of strongly connected urban regions, or communities, in the network space yield geographically cohesive, non-overlapping urban areas that delineate the non-administrative anthropographic urban boundaries of Great Britain.
The technique was applied at the national scale (Great Britain) and the municipal scale (the London metropolis). 
While our results corresponded well to the administrative boundaries, many unexpected and interesting boundaries were identified.

\linenumbers
\section*{Introduction}
Official urban boundaries are defined by government agencies for political and administrative purposes.
Urban environments are conceptualized as spaces that are recreated and formed by human activities~\cite{schliephake}.
A fundamental question when using the administrative, ``top-down'', approach for defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
These interactions can take the form of trade, commerce, social connections, and political activity.
Urban boundaries that respect the human interaction space can be very import to city planning, traffic management and resource allocation~\cite{lynch1960,jiang2015,liu2015,long2015}.
Many studies adopt a ``bottom-up'' approach to urban boundary delineation; where the geographic space is partitioned into small units and each unit is modeled as a node within a network structure.
A suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interaction among the nodes~\cite{lancichinetti2009}.
Different social and physical human interactions were considered to establish the edges of the network connecting the nodes.
For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in the United Kingdom~\cite{ratti2010}.
% does ratti or sobolevsky argue the following... who are "the authors"?
Extending the previous method to different countries~\cite{sobolevsky2013}, the authors argue, yields cohesive geographic divisions that mark the socio-economic boundaries. 
% I think these citations should expand to include the author's names, not just [9].
While~\cite{kallus2015} use social ties of Twitter users to identify cohesive regions for different countries across the world, the authors found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.

In this study, we describe a novel approach to delineate urban boundaries based on the movements of 
Twitter users extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the country level)~\cite{hawelka,jurdak2015}.
We argue here that Twitter user mobility patterns provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation. 
A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in the United Kingdom. 
In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity 
% I think UK calls them postal codes and not zip codes
that is limited to the postal code level~\cite{thiemann}.  % everything has sparsity at some scale...

We delineated the geography of urban boundaries in the United Kingdom by imposing a virtual fishnet over the British Isles. % Great Britain is, itself, an island.
Twitter user movements were used to establish the connections between the fishnet's cells to form a connectivity network, where each cell acts as a node within the network.
We applied the map equation algorithm~\cite{domenico2015} to partition the network and associate geographic regions.
The map equation algorithm was selected to avoid the inherent resolution problem~\cite{fortunato2007} of the common modularity maximization method~\cite{newman2006}. 
We found that the collective mobility patterns of Twitter users in the United Kingdom are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points. 
The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in the United Kingdom.
Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. It provides a new understanding of the interaction between human activity and urban structures.

\section*{Materials and Methods}
\subsection*{Overview}
We use large-scale Twitter user spatial interactions inferred from the collective mobility patterns of Twitter users to delineate urban boundaries in Great Britain.
A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\cite{gonzalez2008}.
This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two recorded locations is one month.
To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the British Isles.
Twitter user movements were then used to establish the connectivity between fishnet cells to form a connectivity network where each cell is considered a node within the network. 
Finally, by detecting strongly connected clusters in the network space using community detection methods~\cite{coscia2011}, we are able to reveal urban boundaries within the geographic space. 
An overview of the approach is illustrated in Fig.~\ref{S1_Fig} and the details are presented in the following sections.

\begin{figure}[ht]
\includegraphics[width=1\linewidth]{./figure/PNG/S1_overview_Fig_2}
\caption{{\bf An overview for delineating urban boundaries from Twitter user movements}}
\label{S1_Fig}
\end{figure}

\subsection*{Geo-located Twitter Data}
A geo-located tweet is a Twitter message with an additional geo-tag expressed as a pair of geographical coordinates that represent the location from which the tweet was sent.
For this study, geo-located tweets were collected using the Twitter Streaming API (\url{https://dev.twitter.com/streaming/overview}) by supplying a geographical bounding box to retrieve all the  geo-located tweets within an area of interest.
% is it the entire UK or the British Isles? It is not Great Britain.
To ensure complete coverage of the United Kingdom, we set the bounding box to the British Isles using the lower left and upper right coordinates (49.497, -14.854), (61.186, 2.637) respectively. This does include part of France.  % ireland is part of the british isles
We implemented a data crawler to continuously collect 7-months of data (June $1^{st}$ -- December $31^{st}$, 2014) resulting in over 101.8 million tweets with a total data volume of 60 GB which we restrict to 69 million based on a process outlined below. 
To showcase the overall spatial coverage of the collected geo-located tweets, a density map of the tweet locations in British Isles for July 2014 is shown in Fig.~\ref{S2_Fig}.
The collected point visualization reveals the geography of cities. Notice the clusters with higher densities of tweets that correspond to the locations of major cities.

\begin{figure}[ht]
\includegraphics[width=0.7\linewidth]{./figure/PNG/S2_twitter_density_Fig_1}
\caption{{\bf A density map of the Twitter user locations for July 2014}}
\label{S2_Fig}
\end{figure}

To verify the collected tweets are from human users, the raw tweets were further filtered using the following steps. 
First we removed the duplicated messages in the dataset.
Next, we removed non-human users based on unusual relocation speed \cite{hawelka,jurdak2015}. 
We adopted a relocation speed threshold of 240 m/s as used by \cite{jurdak2015}. 
We examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold.
Because the original location information embedded in the geo-tag is given in units of latitude and longitude, we projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations. 
Finally, we used the geographical boundary of the United Kingdom, which is derived from Office for National Statistics (ONS) of UK (\url{http://www.ons.gov.uk/ons}), to further restrict the remaining tweets to be ``domestic".
Based on these restrictions, the filtered dataset for the following study contains 69,847,497 tweets made by 1,153,891 twitter users.

@@

\subsection*{A network of large-scale Twitter user spatial interactions}
Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns. 
Some urban regions are more strongly connected to each other than other urban regions.
Therefore, this study connects urban regions when a twitter user begins in one region and ends in another region.
These connections can be represented by an origin-destination (OD) matrix based on the collective Twitter user displacement within the dataset.
This OD matrix is essentially a mathematical representation of a weighted directed graph $G\equiv\langle V, E_{w}\rangle$ where $V$ is a set of spatial nodes corresponding to the underlying urban regions and $E_{w}$ is a set of edges representing the connections between a pair of nodes and the corresponding weights that are assigned to the accumulated volume of Twitter user movement.

To build our spatial network at the kingdom level, we had to determine the basic units to serve as spatial nodes of the connectivity network of urban regions.
Previous studies have suggested equi-distant spatial tessellation to generate nodes, which uses voronoi polygons to partition the space based on the collected points~\cite{rinzivillo2012,zhong2014}. 
This approach demonstrates improvements for estimating the locations of mobile phone records based on the cell tower triangulation~\cite{gonzalez2008,qian2013}.
However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\cite{sakaki2010,zandbergen2009}.
Another popular approach is to partition the space into a grid of spatial pixels~\cite{liuPopMobility,ratti2010}.
However, the size of the cell can potentially lead to biases due to the Modifiable Area Unit Problem (MAUP)~\cite{openshaw1984,wong2009}. To compare our investigation with the findings of similar studies, and avoid subjectively deciding the cell size, we performed a statistical analysis of Twitter user mobility patterns in the United Kingdom and measured the distribution of collective Twitter user displacements and the radius of gyrations of individuals \cite{gonzalez2008,jurdak2015}.
The radius of gyration is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008}, which is defined as Eq. \eqref{eq:2}:
\begin{equation} \label{eq:2}
r_{g} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(p_{i} -  p_{centroid})^{2}}, \textrm{where}\hspace{1ex} p_{centroid} = \frac{1}{n}\sum_{i=1}^{n}p_{i}
\end{equation}
\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
By examining the probability distributions of the radius of gyration, also known as the spatial dispersal kernel $P(r_g)$~\cite{brockmann2006}, we chose 10 km as the cell size to quantify the spatial coverage of the majority of Twitter users in the United Kingdom (Fig.~\ref{S4_Fig} - c, with details shown in the next section). 
Thus, we created a fishnet with 2784 10-km size cells.
The cells of the fishnet act as proxies to represent individuals' spatial coverage areas to focus more on the inter-connectivity among cells and identify strongly connected cell clusters.

\subsection*{Community structure of the spatial networks}
Based on the derived spatial network, which is a directed weighted graph, we further determined clusters of strongly connected spatial nodes, known as communities, in the graph space~\cite{coscia2011}. 
There are a variety of community detection algorithms that produce different results depending the definition of community within the network~\cite{coscia2011}.
A common community detection method is based on modularity maximization~\cite{newman2006}, seen in previous studies~\cite{hawelka,ratti2010,song2012}.
However, such an approach is often problematic: it is found to have an inherent resolution problem, where small communities are either ignored~\cite{fortunato2007} or assigned with high modularity scores \cite{guimera2004}; and it is found to produce less informative partitions in many empirical networks~\cite{good2010}.
Since our graph is a directed weighted graph, the alternative community detection library documented in the literature is Infomap~\cite{domenico2015,rosvall2008}, which is considered to produce better community detection results~\cite{lancichinetti2009}.

%NOTE: the random walk should be better introduced or defined. This is slightly confusing.
Infomap uses the map equation~\cite{rosvall2010} to represent the probability of flow of random walks within information systems.
It identifies communities by minimizing the expected description length of the trajectory of a random walker, which is shown below:
\begin{equation} \label{eq:1}
L(M)=qH(Q) + \sum_{i=1}^{m} p_{i}H(p_{i})
\end{equation}

In Eq. \eqref{eq:1} , $L(M)$ consists of two terms: qH(Q) is the entropy of the movement among clusters and $ \sum_{i=1}^{m} p_{i}H(p_{i})$ is the entropy of movement within clusters. 
To be more specific, q is the probability that a random walker jumps from one cluster to another, while $p_i$ is the probability of the in-cluster movement of cluster i.
In this regard, this algorithm can be intuitively tailored to describe strongly connected clusters of urban regions based on Twitter user movement.
The detailed literatures and implementations of Infomap can be found on this website (\url{http://mapequation.org}).
Note that Infomap is capable of performing multi-level community detection~\cite{domenico2015}, but we only use the algorithm to produce our most detailed community structures
to examine groups of strongly connected urban regions.

\section*{Results and Discussion}
\subsection*{Collective Mobility Patterns of Twitter Users in Great Britain}
We first modeled different aspects of the collective mobility patterns of Twitter users.
These patterns include: the number of visited locations per user,  the collective user displacements, and the radius of gyration of individuals in order to identify natural breaks in user travel patterns.
We then used these natural breaks within the mobility patterns to partition the geographic space of the United Kingdom into fine-grained cells and established the connectivity among these cells to redraw non-administrative anthropographic urban boundaries.

@@

\begin{figure}[ht]
\includegraphics[width=1.0\linewidth]{./figure/PNG/S3_visitation}
\caption{{\bf Cumulative distribution of the number of locations visited by each Twitter user during different timespan}}
\label{S3_Fig}
\end{figure}

We further studied two aspects of the Twitter user mobility patterns: the distribution of Twitter user displacement and the radius of gyration. 
Twitter user displacement refers to the distance between two consecutive locations in a user's trajectory using a straight-line distance metric.
The radius of gyration describes the deviation of distance from the center of mass in a user's trajectory.
The probability distributions of the collective user displacement $P(d)$ and radius of gyration $P(r_g)$ are presented in Fig.~\ref{S4_Fig}, where the fitting method for identifying different distance ranges is derived from~\cite{jurdak2015}.
The probability distribution of the collective displacements can be approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10m, 70m] (accounting for 3 $\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [70m, 70km] (93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 70km] (4 $\%$ of the population). 
The displacement distance between 70m and 100km can be further approximated by two power law distributions with a cut-off point at 4km (55$\%$ distances are less than 4km and 40$\%$ distances between 4km and 100km), which indicates the urban movement captured by the geo-located Twitter data to reveal two different modes: inter-city and intra-city movement. 
In short, these fitting functions suggest the existence of multi-scale or multi-modal urban movements captured from Twitter users in the United Kingdom, which means the geographically cohesive, non-overlapping urban areas identified in the next section are not just a result of short distance movement but emerge naturally from the broader Twitter user mobility pattern.
Note that a similar multiphase pattern was observed in Twitter user displacements in Australia, but with slightly different distance ranges\cite{jurdak2015}.

>>>>

% tGISguide.tex
% v3.4 released April 2009

\documentclass[]{tGIS2e}
% line numbers
\usepackage[right]{lineno}

%\citestyle{tGIS}

\begin{document}

%\doi{10.1080/1365881YYxxxxxxxx}
%\issn{1362-3087} \issnp{1365-8816} \jvol{00} \jnum{00} \jyear{2009} %\jmonth{February}

%\markboth{Taylor \& Francis and I.T. Consultant}{International Journal of Geographical Information Science}

\articletype{RESEARCH ARTICLE}

\title{{\itshape Delineate urban boundaries in Great Britain from the network of Twitter user spatial interactions} }
\maketitle

\begin{abstract}
Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns.
Defining the boundaries of urban regions is important to city planning, traffic management and resource allocation.
Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's daily interactions with the urban space in their intra- and inter regional activities.
In this study, we presented a method to redraw urban boundaries based upon human interaction with the physical space.
Specifically, we delineated the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million Twitter messages.
Our study connects human mobility research with the delineation of non-administrative anthropographic urban boundaries based on Twitter user spatial interactions, which provides a new understanding of the interactions between urban structure and human activity.
We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
The result of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas that provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
The technique was applied to both national scale (Great Britain) and municipal scale (the London metropolis). 
While our results corresponded well to the administrative boundaries, many unexpected and interesting boundaries were identified.
\newline

\noindent{\bf{Keywords:}} mobility pattern, urban boundary, spatial interaction, spatial network, community structure
\end{abstract}
\linenumbers
\section{Introduction}
\markboth{International Journal of Geographical Information Science}{International Journal of Geographical Information Science}
Official urban boundaries are defined by government agencies for political and administrative purposes.
Urban environments are conceptualized as spaces that are recreated and formed by human activities~\citep{schliephake}.
A fundamental question when using the administrative, ``top-down'', approach to defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
These interactions can take the form of trade, commerce, social connections, and political activity across the borders.
Urban boundaries that respect the human interaction space can be very import to city planning, traffic management and resource allocation~\citep{lynch1960,jiang2015,liu2015,long2015}.
Many studies adopt a ``bottom-up'' approach to urban boundary delineation, where the geographic space is partitioned into small units and each unit is modeled as a node within a network structure.
A suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interaction among the nodes~\cite{lancichinetti2009}.
Different social and physical human interactions were considered to establish the edges of the network connecting the nodes.
For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in Great Britain~\cite{ratti2010}.
Extending the previous method to different countries~\cite{sobolevsky2013}, the authors argue that this method yields cohesive geographic divisions that follow the socio-economic boundaries.
While other researchers use social ties of Twitter users to identify cohesive regions for different countries across the world~\cite{kallus2015}, they found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.

In this study, we describe a novel approach to delineating urban boundaries based on the movements of 
Twitter users extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the country level)~\cite{hawelka,jurdak2015}.
We argue here that Twitter user mobility patterns provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation. 
A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in Great Britain. 
In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity that is limited to the postal code level~\cite{thiemann}.

We delineated the geography of urban boundaries in Great Britain by imposing a virtual fishnet over the islands of Great Britain.
Twitter user movements were used to establish the connections between the fishnet's cells to form a connectivity network, where each cell acts as a node within the network.
We applied the map equation algorithm~\citep{domenico2015} to partition the network and associate geographic regions.
The map equation algorithm was selected to avoid the inherent resolution problem~\cite{fortunato2007} of the common modularity maximization method~\citep{newman2006}. 
We found that the collective mobility patterns of Twitter users in Great Britain are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points. 
The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of the urban space in Great Britain.
Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. 
It provides a new understanding of the interactions between human activity and urban structures.

\section{Materials and Methods}
\subsection{Overview}
We use large-scale Twitter user spatial interactions inferred from the collective mobility patterns of Twitter users to delineate urban boundaries in Great Britain.
A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\cite{gonzalez2008}.
This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two recorded locations is one month.
To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the islands of Great Britain.
Twitter user movements were then used to establish the connectivity between fishnet cells to form a connectivity network where each cell is considered a node within the network. 
Finally, by detecting strongly connected clusters in the network space using community detection methods~\cite{coscia2011}, we were able to reveal urban boundaries within the geographic space. 
An overview of the approach is illustrated in Fig.~\ref{S1_Fig} and the details are presented in the following sections.

%\begin{figure}[ht]
%\includegraphics[width=1\linewidth]{./figure/S1_overview_Fig_2}
%\caption{{\bf An overview for delineating urban boundaries from Twitter user movements}}
%\label{S1_Fig}
%\end{figure}

\begin{figure}[ht]
\begin{center}
\vspace{36pt}
\includegraphics[width=1\linewidth]{./figure/S1_overview_Fig_2}
\caption{\bfseries{An overview for delineating urban boundaries from Twitter user movements}}
\label{S1_Fig}
\end{center}
\end{figure}

\subsection{Geo-located Twitter Data}
A geo-located tweet is a Twitter message with an additional geo-tag expressed as a pair of geographical coordinates that represent the location from which the tweet was sent.
For this study, geo-located tweets were collected using the Twitter Streaming API (
{\tt{https://dev.twitter.com/streaming/overview}}) by supplying a geographical bounding box to retrieve all the  geo-located tweets within an area of interest. To ensure complete coverage of Great Britain, we set the bounding box to the British Isles using the lower left and upper right coordinates (49.497, -14.854), (61.186, 2.637) respectively. This does include the whole of Ireland part of France.
We implemented a data crawler to continuously collect 7-months of data (June $1^{st}$ -- December $31^{st}$, 2014) resulting in over 101.8 million tweets with a total data volume of 60 GB, which we restrict to 69 million based on a process outlined below. 
To showcase the overall spatial coverage of the collected geo-located tweets, a density map of the tweet locations in British Isles for July 2014 is shown in Fig.~\ref{S2_Fig}.
The collected point visualization reveals the geography of cities.
Notice the clusters with higher densities of tweets correspond to the locations of major cities.

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.8\linewidth]{./figure/S2_twitter_density_Fig_1}
\caption{\bfseries{A density map of the Twitter user locations for July 2014}}
\label{S2_Fig}
\end{center}
\end{figure}

To verify the collected tweets are from human users, the raw tweets were further filtered using the following steps. 
First we removed the duplicated messages in the dataset.
Next, we removed non-human users based on unusual relocation speed \cite{hawelka,jurdak2015}. 
We adopted a relocation speed threshold of 240 m/s as used by \cite{jurdak2015}. 
We examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold.
Because the original location information embedded in the geo-tag is given in units of latitude and longitude, we projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations. 
Finally, we used the geographical boundary of Great Britain, which is derived from Office for National Statistics (ONS) of UK ({\tt{http://www.ons.gov.uk/ons}}), to further restrict the remaining tweets to be ``domestic".
Based on these restrictions, the filtered dataset for the following study contains 69,847,497 tweets made by 1,153,891 twitter users.

@@

\subsection{A network of large-scale Twitter user spatial interactions}
Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns. 
Some urban regions are more strongly connected to each other than other urban regions.
Therefore, this study connects urban regions when a twitter user's movement begins in one region and ends in another region.
These connections can be represented by an origin-destination (OD) matrix based on the collective Twitter user displacements within the dataset.
This OD matrix is essentially a mathematical representation of a weighted directed graph $G\equiv\langle V, E_{w}\rangle$, where $V$ is a set of spatial nodes corresponding to the underlying urban regions and $E_{w}$ is a set of edges representing the connections between a pair of nodes and the corresponding weights are assigned by the accumulated volume of Twitter user movements.

To build our spatial network at a national level, we had to determine the basic units to serve as spatial nodes of the connectivity network of urban regions.
Previous studies have suggested equi-distant spatial tessellation to generate nodes, which uses voronoi polygons to partition the space based on the collected points~\cite{rinzivillo2012,zhong2014}. 
This approach demonstrates improvements for estimating the locations of mobile phone records based on the cell tower triangulation~\cite{gonzalez2008,qian2013}.
However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\cite{sakaki2010,zandbergen2009}.
Another popular approach is to partition the space into a grid of spatial pixels~\cite{liuPopMobility,ratti2010}.
However, the size of the cell can potentially lead to biases due to the Modifiable Area Unit Problem (MAUP)~\cite{openshaw1984,wong2009}, where different choices of unit size can lead to significant variant findings. 
To compare our investigation with the findings of similar studies, and avoid subjectively deciding the cell size, we performed statistical analysis of Twitter user mobility patterns in Great Britain and measured the distribution of collective Twitter user displacements and the radius of gyrations of individuals \cite{gonzalez2008,jurdak2015}.
The radius of gyration is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008}, which is defined as Eq. \eqref{eq:2}:

\begin{equation} \label{eq:2}
r_{g} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(p_{i} -  p_{centroid})^{2}}, \textrm{where}\hspace{1ex} p_{centroid} = \frac{1}{n}\sum_{i=1}^{n}p_{i}
\end{equation}

\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
By examining the probability distributions of the radius of gyration, also known as the spatial dispersal kernel $P(r_g)$~\cite{brockmann2006}, we chose 10 km as the cell size to quantify the spatial coverage of the majority of Twitter users in Great Britain (Fig.~\ref{S4_Fig} - c, with details shown in the next section). 
Thus, we created a fishnet with 2784 10-km size cells.
The cells of the fishnet act as proxies to represent individuals' spatial coverage areas to focus more on the inter-connectivity among cells and identify strongly connected cell clusters.

\subsection{Community structure of the spatial networks}
Based on the derived spatial network, which is a directed weighted graph, we further determined clusters of strongly connected spatial nodes, known as communities, in the graph space~\cite{coscia2011}. 
There are a variety of community detection algorithms that produce different results depending the definition of community within the network~\cite{coscia2011}.
A common community detection method is based on modularity maximization~\cite{newman2006}, seen in previous studies~\cite{hawelka,ratti2010,song2012}.
However, such an approach is often problematic: it is found to have an inherent resolution problem, where small communities are either ignored~\cite{fortunato2007} or assigned with high modularity scores \cite{guimera2004}; and it is found to produce less informative partitions in many empirical networks~\cite{good2010}.
Since our graph is a directed weighted graph, the alternative community detection library documented in the literature is Infomap~\cite{domenico2015,rosvall2008}, which is considered to produce better community detection results~\cite{lancichinetti2009}.

Infomap uses the map equation~\cite{rosvall2010} to represent the probability of flow of random walks within information systems~\cite{rosvall2008}.
It identifies communities by minimizing the expected description length of the trajectory of a random walker, which is shown below:

\begin{equation} \label{eq:1}
L(M)=qH(Q) + \sum_{i=1}^{m} p_{i}H(p_{i})
\end{equation}

In Eq. \eqref{eq:1} , $L(M)$ consists of two terms: qH(Q) is the entropy of the movement among clusters and $ \sum_{i=1}^{m} p_{i}H(p_{i})$ is the entropy of movement within clusters. 
To be more specific, q is the probability that a random walker jumps from one cluster to another, while $p_i$ is the probability of the in-cluster movement of cluster i.
In this regard, this algorithm can be intuitively tailored to describe strongly connected clusters of urban regions based on Twitter user movement.
The detailed literatures and implementations of Infomap can be found on this website ({\tt{http://mapequation.org}}).
Note that Infomap is capable of performing multi-level community detection~\cite{domenico2015}, but we only use the algorithm to produce our most detailed community structures
to examine groups of strongly connected urban regions.

\section{Results and Discussion}
\subsection{Collective Mobility Patterns of Twitter Users in Great Britain}
We first modeled different aspects of the collective mobility patterns of Twitter users.
These patterns include: the number of visited locations per user,  the collective user displacements, and the radius of gyration of individuals in order to identify natural breaks in user travel patterns.
We then used these natural breaks within the mobility patterns to partition the geographic space of Great Britain into fine-grained cells and established the connectivity among these cells to redraw non-administrative anthropographic urban boundaries.

@@

\begin{figure}[ht]
\includegraphics[width=1.0\linewidth]{./figure/S3_visitation}
\caption{ \bfseries{Cumulative distribution of the number of locations visited by each Twitter user during different timespan}}
\label{S3_Fig}
\end{figure}

We further studied two aspects of the Twitter user mobility patterns: the distribution of Twitter user displacement and the radius of gyration. 
Twitter user displacement refers to the distance between two consecutive locations in a user's trajectory using a straight-line distance metric.
The radius of gyration describes the deviation of distance from the center of mass in a user's trajectory.
The probability distributions of the collective user displacement $P(d)$ and radius of gyration $P(r_g)$ are presented in Fig.~\ref{S4_Fig}, where the fitting method for identifying different distance ranges is derived from~\cite{jurdak2015}.
The probability distribution of the collective displacements can be approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10m, 70m] (accounting for 3 $\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [70m, 70km] (93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 70km] (4 $\%$ of the population). 
The displacement distance between 70m and 100km can be further approximated by two power law distributions with a cut-off point at 4km (55$\%$ distances are less than 4km and 40$\%$ distances between 4km and 100km), which indicates the urban movement captured by the geo-located Twitter data to reveal two different modes: inter-city and intra-city movement. 
In short, these fitting functions suggest the existence of multi-scale or multi-modal urban movements captured from Twitter users in Great Britain, which means the geographically cohesive, non-overlapping urban areas identified in the next section are not just a result of short distance movement but emerge naturally from the broader Twitter user mobility pattern.
Note that a similar multiphase pattern was observed in Twitter user displacements in Australia, but with slightly different distance ranges\cite{jurdak2015}.
